### 2023-09-10 writing/manuscript.Rmd
remove word "test" from .rmd chunk name
raw and processed data

```{r test-mega-fig, results= "asis", fig.pos = "H", fig.width = 9, fig.height = 9, fig.cap="\\textbf{Fig. 1 | In a large global sample of participants, we find negligibly small sex differences in general musical ability. A} Geographic spread of participants who completed music perception tests. The shading of each country indicates the number of participants who self-reported that country as their location. \\textbf{B} In an aggregate measure of general musical ability (composed of measures \\textbf{C, D, E}), there is a negligibly small difference between men and women's scores. The shaded areas represent kernel density estimations."}
listener_map <- readPNG("../viz/DIFF_listeners_manuallycleaned.png")
listener_map <- ggdraw() + draw_image(listener_map)

@@

\newpage
```{r SItable3 prep}
# SI table detailing all items, their possible responses, and how the verbal responses were coded numerically
# MB: deliberately loading in plyr here, late, to not interfere with dplyr verbs higher up
library(plyr)
SI_dat <- readRDS("../data/clean-person-level-data.rds") %>% 
  select("music_tap", "out_of_tune", "music_skill", "music_listen", "lessons_enjoy", "lessons_peers", "theory_training", "music_feel", "music_listen_time", "familiarity_tradmusic") %>%
  # mutate to character to allow pivot longer
  mutate(music_listen = as.character(music_listen)) %>% 
  pivot_longer(everything(), names_to = "item", values_to = "answer") %>%
  filter(!is.na(answer)) %>%
  unique()

>>>>

```{r mega-fig, results= "asis", fig.pos = "H", fig.width = 9, fig.height = 9, fig.cap="\\textbf{Fig. 1 | In a large global sample of participants, we find negligibly small sex differences in general musical ability. A} Geographic spread of participants who completed music perception tests. The shading of each country indicates the number of participants who self-reported that country as their location. \\textbf{B} In an aggregate measure of general musical ability (composed of measures \\textbf{C, D, E}), there is a negligibly small difference between men and women's scores. The shaded areas represent kernel density estimations."}
listener_map <- readPNG("../viz/DIFF_listeners_manuallycleaned.png")
listener_map <- ggdraw() + draw_image(listener_map)

@@

\newpage
```{r SItable3 prep}
# SI table detailing all items, their possible responses, and how the verbal responses were coded numerically
# MB: deliberately loading in plyr here, late, to not interfere with dplyr verbs higher up
library(plyr)
SI_dat <- readRDS("../data/clean-person-level-data-filtered.rds") %>% 
  # mutate to character to allow pivot longer
  mutate(music_listen = as.character(music_listen)) %>% 
  pivot_longer(everything(), names_to = "item", values_to = "answer") %>%
  filter(!is.na(answer)) %>%
  unique()
